Shaping strategy in core and flake industry：Standardized manufacturing of QSY (North China) faceted spheroids

### 2025-05-20 analysis/paper/paper.qmd
update file paths

library(data.table)
library(NISTunits)
library(circular)
library(ggpubr)
library(ggalt)
library(ggplot2)
library(stringr)
library(ggtern)
library(dplyr)
source('McPherron_2018.r')
source('get_coordinates.r')
source('vector_stats.r')

@@

# 遍历文件夹中的文本文件
folder_path <- "C:/Users/27086/Desktop/Sam Lin-orientation analysis/Lin_et_al_Core_scar_orientation_Data_and_R_code/Data_and_R_code/QSY_A"
temp_file_list <- list.files(folder_path, pattern = "\\.txt$")  # 只列出 .txt 文件

@@

# 保存为 CSV
write.csv(benn.output, "benn_output.csv", row.names = FALSE)
```

@@

ggsave("benn_ternary_plot.jpg", width = 8, height = 6, dpi = 300)

@@

>>>>

library(data.table)
library(NISTunits)
library(circular)
library(ggpubr)
library(ggalt)
library(ggplot2)
library(stringr)
library(ggtern)
library(dplyr)
library(here)
source(here('analysis/paper/scripts/McPherron_2018.r'))
source(here('analysis/paper/scripts/get_coordinates.r'))
source(here('analysis/paper/scripts/vector_stats.r'))
```

@@

# 遍历文件夹中的文本文件
folder_path <- here("analysis/data/QSY_A")
temp_file_list <- list.files(folder_path, pattern = "\\.txt$")  # 只列出 .txt 文件

@@

# 保存为 CSV
write.csv(benn.output,
          here("analysis/data/benn_output.csv"), row.names = FALSE)
```

@@

ggsave(here("analysis/figures/benn_ternary_plot.jpg"), 
       width = 8, 
       height = 6, 
       dpi = 300)

@@

```{r}
#| label: fig-myfig
#| fig-cap: "the text of the captions. "
#| fig-height: 4

knitr::include_graphics(here::here("analysis/figures/thefigure.png"))
```
